Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-15 examples_C.tex
+

  pte_t *pdp = pte_get_next_table(pml4_entry); /*(*\label{line:first_getnext_call}*) save the physical next table address in rax*/

@@

  /*pte_get_next_table may have allocated a new page, updating entry*/

@@

  /*... Similar assembly & proofs for levels 3 and 2*/

@@

  /* return address of L1 entry, similar index computation*/

>>>>

  pte_t *pdp = pte_get_next_table(pml4_entry); (*\label{line:first_getnext_call}*) 

@@

  /*pte_get_next_table may have allocated a new page which updates entry*/

@@

  /*Similar steps & proofs for levels 3 and 2*/

@@

  /*Return the address of L1 entry with a similar index computation*/
